### 2019-08-02 paper/paper.tex
Tie-breakers

After passing our input sequence through BERT, we use a concatenation of the final hidden states matching the classifier tokens as the sequence representation. We also learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair.

@@

@@

\subsection{Learning}

>>>>

After passing our input sequence through BERT, we use a concatenation of the final hidden states matching the classifier tokens as the sequence representation. We learn as a parameter a vector whose dot product with the sequence representation is the score for the given answer pair.

@@

% TODO: add a markov chain graph here

@@

\subsubsection{Tie-breakers}

This is not a method on its own, but it can be used on top of the other ones.
Essentially, we can assert a "Certainty Threshold" on the probabilities obtained from the other methods, a rate between two probabilities under which we consider our prediction to be uncertain/unstable.
If such a scenario arises, we then resort to choosing between the two highest-scored choices directly - that is, by looking at the score given to the pair and deciding accordingly.

Note that this change does not cause a change in the probabilities themselves, it only changes the predicted answer. As such, it does not cause a change in the measured loss, thus does not affect the learned parameters. It does change, however, the measured accuracy, which means that when learning parameters we will favor a parameter set that maximizes the accuracy given this change.

\section{Experiments and Results}

As our model deviates greatly from the assumptions that were made when the original BERT weights were trained, it is understanable that our model required more epochs to converge than the amount of epochs the original paper used when fine-tuning to the question answering task.
We should also note that because each sample now consists of much more input sequences (the original model had one sequence per possible answer, our model has one sequence per possible answer \textbf{pair}), we are now more limited in our batch size, as the GPU has to hold the entire batch simultaneously. This problem can be mitigated by using gradient accumulation.

Our models were trained in parts.
In the first part, we trained solely on the dataset alterations part, without intergrating the pair scores. That is, our model was trained directly on identifying the better answer in a pair
